On the spatial aggregation of condition metrics for ecosystem accounting

### 2025-12-01 manuscript/manuscript.qmd
conclusion

```{r fig-pathways}
#| fig-cap: |
#|   Flowchart showing pathways for the spatial aggregation of variables in ecosystem condition accounting. Normalisation refers to the steps that make a variable conform to the definition of an indicator in SEEA EA, which may include some, but not necessarily all, of the steps scale, truncate and transform.
#| out-width: 400
#| echo: false
knitr::include_graphics("../img/aggregationPathways.png")
```

@@

# Conclusion

>>>>

```{r fig-pathways}
#| fig-cap: |
#|   Flowchart showing  a selection of nine possible pathways for the spatial aggregation of variables in ecosystem condition accounting. Normalisation refers to the steps that make a variable conform to the definition of an indicator in SEEA EA, which may include some, but not necessarily all, of the steps scale, truncate and transform. The pathway description used the standardised shorthand aggregation athway terminology, where trunc. = truncation, trans. = transformation, sp. agg. = spatial aggregation, proj. = project (extrapolation or interpolation), sample = sub-sampling from a larger dataset, th. agg. = thematic aggregation.
#| out-width: 400
#| echo: false
knitr::include_graphics("../img/aggregationPathways.png")
```

@@

# Conclusion
This paper has described the reasons why we need to do spatial generalisation in ecosystem accounting, and 
clarified several misconscptions about this process. 
We have showed that indeitical raw data, when spatially aggregated through different pathways, can yield fundamentally different types of information about ecosystems condition. 
The recommendations offered here is intended to help researchers 
design ecosystem condition metrics that better align 
with the type of information they aim to communicate from the data, 
while also improving transparency through the use of a standardised terminology.
With a clearer understanding of the challenges inherrent to spatial generalisation,
we that hope future ecosystem condition accounts will be more internally consistent, more comparable between each other, and less susceptible to unintended mathematical artefacts.
